Predicting Solid State Material Platforms for Quantum Technologies

### 2021-12-17 paper.tex
Updates from Overleaf

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{physics}
\usepackage{lipsum}
% \usepackage{subfig} %not compatible with subcaption
% \usepackage{braket}
\usepackage{siunitx}
\usepackage{color}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tikz,pgfplots}
\usepackage{makecell}
\captionsetup[table]{skip=10pt}
\pgfplotsset{compat=1.17}
\sisetup{separate-uncertainty}
\usepackage{hyperref} 
\usepackage{longtable}

@@

%We have developed data extraction tools for numerous material science databases, and constructed over $4800$ physics-informed features for a data set consisting of more than $25000$ materials. Furthermore, we have developed and implemented three data mining approaches, termed \textit{the Ferrenti approach}, \textit{the augmented Ferrenti approach} and \textit{the intuitive approach} for defining three distinct training sets for the supervised machine learning algorithms logistic regression, decision tree, random forest and gradient boost to be trained on.
Data extraction tools have been developed for a number of materials science databases resulting in a data set consisting of over $25.000$ materials. The information from the databases was converted into nearly $5000$ physics-informed features. Furthermore, we have developed and implemented three different approaches for the data mining process: \textit{The Ferrenti approach}, \textit{the augmented Ferrenti approach}, and \textit{the intuitive approach}. 
%Rename intuitive approach! To what? 
%Options include stringent, strict, cherry-picked, informed and intuitive. 
The three approaches define distinct training sets for the supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting.

@@

\subsubsection*{The Ferrenti approach}
The first approach to defining a training set is based on the criteria proposed by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}.
They suggest a data mining process consisting of four stages by systematically evaluating the suitability of host materials from the Materials Project. In this framework, we label \textbf{suitable} candidates by the following steps:
%MHJ how do we cite the  ICSD data? No ref as of now
\begin{enumerate}
    \item Include materials that;
    \begin{itemize}
        \item contain elements with more than $50 \ \%$ natural abundance of spin zero  isotopes,
        \item crystallize in non-polar space groups,
        \item are present in the ICSD database (the world's largest database for completely identified inorganic crystal structures), and
        \item are calculated to be nonmagnetic. 
    \end{itemize}
    \item Pragmatically remove toxic, radioactive and otherwise ``difficult'' materials;
    \begin{itemize}
        \item exclude Th, U, Cd and Hg because they are radioactive and/or toxic in most stable forms,
        \item exclude any rare-earth metals (because of the difficulty of obtaining pure materials free of isotopes with nuclear spin) and noble gases (due to the lack of stable solid phases),
        \item exclude transition metal elements with unpaired electrons like Fe and Ni because of their paramagnetism. Ru and Os are also removed because they only exist in the data as complex cluster structures. 
    \end{itemize}
    \item Include only materials with a band gap larger than $0.5$~eV calculated using DFT and the PBE functional. The value of $0.5$~eV was chosen to match that typically predicted for silicon by PBE-level DFT calculations. 
    \item Ensure that energy above hull is less than $0.2$~eV per atom.
\end{enumerate}

@@

\begin{figure}[h] %!tbp
    \centering
    \begin{subfigure}{0.3\textwidth}
        \centering
        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/01-ferrenti-approach-v2.pdf}
    \end{subfigure}%
    \begin{subfigure}{0.3\textwidth}
        \centering
        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/02-augmented-ferrenti-approach.pdf}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
        \centering
        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/03-insightful-approach-v2.pdf}
    \end{subfigure}
    %\vspace*{-95mm}
    \caption{Two-dimensional scatter plots for the three different approaches. We have identified the two eigenvectors corresponding to the two largest eigenvalues of the covariance-matrix, that is, the two most important principal components (PC1 and PC2) of the initial data from the Materials Project query. Then, we have transformed the three training sets resulting from the three approaches and visualized them as scatter plots. Green squares display suitable candidates and red triangles represent unsuitable candidates.}
    \label{fig:2dscatterplotpca}
\end{figure}

@@

\begin{figure}[h] %!tbp
    \centering
    \begin{subfigure}{1\textwidth}
        \centering
        %\includegraphics[width=1\textwidth]{figures/histograms/01-02-histogram-.pdf}
        \input{figures/histograms/summary-01-02-histogram-.tex}
    \end{subfigure}%

@@

\section*{Data availability} 
The data sets that support the findings of this study are available online at DOI: 10.5281/zenodo.4633959.

\section*{Code availability} 
The codes employed to develop the machine learning results are available online at 
%https://github.com/ohebbi/predicting-solid-state-qubit-material-hosts 
DOI: 10.5281/zenodo.4633959. 
%Update with new release later).

>>>>

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{physics}
\usepackage{lipsum}
% \usepackage{subfig} %not compatible with subcaption
% \usepackage{braket}
\usepackage{siunitx}
\usepackage{color}
% \usepackage{caption}
\usepackage{subcaption}
\usepackage{tikz,pgfplots}
\usepackage{makecell}
\captionsetup[table]{skip=10pt}
\pgfplotsset{compat=1.17}
\sisetup{separate-uncertainty}
\usepackage{hyperref} 
% \usepackage{longtable}

@@

%We have developed data extraction tools for numerous material science databases, and constructed over $4800$ physics-informed features for a data set consisting of more than $25000$ materials. Furthermore, we have developed and implemented three data mining approaches, termed \textit{the Ferrenti approach}, \textit{the augmented Ferrenti approach} and \textit{the intuitive approach} for defining three distinct training sets for the supervised machine learning algorithms logistic regression, decision tree, random forest and gradient boost to be trained on.
Data extraction tools have been developed for a number of materials science databases resulting in a data set consisting of over $25.000$ materials. The information from the databases was converted into nearly $5000$ physics-informed features. Furthermore, we have developed and implemented three different approaches for the data mining process: \textit{The Ferrenti approach}, \textit{the augmented Ferrenti approach}, and \textit{the intuitive approach}. 
%Rename insightful approach! To what? 
%Options include stringent, strict, cherry-picked, informed and intuitive. 
The three approaches define distinct training sets for the supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting.

@@

\subsubsection*{The Ferrenti approach}
The first approach to defining a training set is based on the criteria proposed by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}.
They suggest a data mining process consisting of four stages by systematically evaluating the suitability of host materials from the Materials Project. In this framework, we label \textbf{suitable} candidates by the following steps:
%MHJ how do we cite the  ICSD data? No ref as of now
\begin{enumerate}
    \item Include materials that;
    \begin{itemize}
        \item contain elements with more than $50 \ \%$ natural abundance of spin zero  isotopes,
        \item crystallize in non-polar space groups,
        \item are present in the ICSD database~\cite{Allen1987} (the world's largest database for completely identified inorganic crystal structures), and
        \item are calculated to be nonmagnetic. 
    \end{itemize}
    \item Pragmatically remove toxic, radioactive and otherwise ``difficult'' materials;
    \begin{itemize}
        \item exclude Th, U, Cd and Hg because they are radioactive and/or toxic in most stable forms,
        \item exclude any rare-earth metals (because of the difficulty of obtaining pure materials free of isotopes with nuclear spin) and noble gases (due to the lack of stable solid phases),
        \item exclude transition metal elements with unpaired electrons like Fe and Ni because of their paramagnetism. Ru and Os are also removed because they only exist in the data as complex cluster structures. 
    \end{itemize}
    \item Include only materials with a band gap larger than $0.5$~eV calculated using DFT and the PBE functional. The value of $0.5$~eV was chosen to match that typically predicted for silicon by PBE-level DFT calculations. 
    \item Ensure that energy above hull is less than $0.2$~eV per atom.
\end{enumerate}

@@

\begin{figure}%[h] %!tbp
    \centering
    \begin{subfigure}{0.3\textwidth}
        \centering
        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/01-ferrenti-approach-v2.pdf}
    \end{subfigure}%
    \begin{subfigure}{0.3\textwidth}
        \centering
        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/02-augmented-ferrenti-approach.pdf}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
        \centering
        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/03-insightful-approach-v2.pdf}
    \end{subfigure}
    %\vspace*{-95mm}
    \caption{Two-dimensional scatter plots for the three different approaches. We have identified the two eigenvectors corresponding to the two largest eigenvalues of the covariance-matrix, that is, the two most important principal components (PC1 and PC2) of the initial data from the Materials Project query. Then, we have transformed the three training sets resulting from the three approaches and visualized them as scatter plots. Green squares display suitable candidates and red triangles represent unsuitable candidates.}
    \label{fig:2dscatterplotpca}
\end{figure}

@@

\begin{figure}%[h] %!tbp
    \centering
    \begin{subfigure}{1\textwidth}
        \centering
        %\includegraphics[width=1\textwidth]{figures/histograms/01-02-histogram-.pdf}
        \input{figures/histograms/summary-01-02-histogram-.tex}
    \end{subfigure}%

@@

\section*{Data availability} 
The data sets that support the findings of this study are available online at \cite{Ohebbi2021}.

\section*{Code availability} 
The codes employed to develop the machine learning results are available online at 
%https://github.com/ohebbi/predicting-solid-state-qubit-material-hosts 
\cite{Ohebbi2021}.
%Update with new release later).
